Network Structure, Efficiency, and Performance in WikiProjects

### 2018-04-10 icwsm-cameraready/wp-eff-perf.tex
Add ICWSM camera-ready version.

@@

Our analysis combines multiple data
sets\footnote{Data and code at https://elplatt.com/a/WikiProject-Eff-Perf}
from the English-language Wikipedia.
For information about edit history, we used a publicly-available data set containing
metadata (time, article id, user) about all edits from July 12, 2006 to December 2, 2015.
We used a custom script to scrape article quality assessments from logs produced
by WP 1.0 Bot for 2279 unique WikiProjects
between May 4, 2006 and December 2, 2015.
Finally, we used a publicly-available database dump of page events (including rename events)
to reconstruct the article id for each title mentioned in the assessment logs.

@@

In this paper, we have described the relationship between the structural properties of WikiProject
coeditor networks, their performance, and their efficiency.
As in other studies, we see a trade-off between performance and efficiency. However, 
some properties, such as low degree, are associated with both higher performance and efficiency.
We also find that the correlations between path length and performance are consistent with a conformity-based
social learning strategy, but not a greedy best-neighbor strategy.
We observe improved performance in more decentralized projects, as has been seen in small-scale lab experiments.
While the performance and efficiency of most previously-studied social learning strategies depend more on path length than
degree,
we have proposed a novel local majority learning strategy that is more realistic, more efficient, and higher performance than
existing strategies.
We observe that in both the local majority strategy and a localized version of
the conformity strategy,
the performance and efficiency of a collaboration can exhibit degree dependence,
and that the direction of that dependence varies with the specific strategy being used.
While additional work is needed to determine causal relationships
and the generalizability of our results,
we have shown evidence that several phenomena predicted by numerical
and small-scale lab experiments are present in a large,
real-world collaboration.
Our results suggest that the success of large-scale collaborations may be aided
by greater decentralization,
consensus or conformity-based decision-making,
and more tightly-knit collaborations between smaller teams.

@@

>>>>

\def\year{2018}\relax
%File: formatting-instruction.tex
\documentclass[letterpaper]{article} %DO NOT CHANGE THIS
\usepackage{aaai18}  %Required
\usepackage{times}  %Required
\usepackage{helvet}  %Required
\usepackage{courier}  %Required
\usepackage{url}  %Required
\usepackage{graphicx}  %Required
\frenchspacing  %Required
\setlength{\pdfpagewidth}{8.5in}  %Required
\setlength{\pdfpageheight}{11in}  %Required
%PDF Info Is Required:
  \pdfinfo{
/Title (Network Structure, Efficiency, and Performance in WikiProjects)
/Author Edward L. Platt and Daniel M. Romero}
\setcounter{secnumdepth}{0}

% Document-specific packages
\usepackage{epigraph}
\usepackage[normal]{threeparttable}
\usepackage{graphicx}
\usepackage{bbding}

% Document-specific definitions
\newcommand{\beq}{\begin{eqnarray}}
\newcommand{\eeq}{\end{eqnarray}}
\newcommand{\+}{\phantom{-}}

 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Network Structure, Efficiency, and Performance in WikiProjects}
%\author{Anonymized \\
%for\\
%blind review
%\And
%Anonymized \\
%for\\
%blind review
\author{Edward L. Platt \\
University of Michigan\\
Ann Arbor, MI\\
elplatt@umich.edu
\And
Daniel M. Romero\\
University of Michigan\\
Ann Arbor, MI\\
drom@umich.edu
}
\maketitle

@@

Our analysis combines multiple data
sets from the English-language Wikipedia \cite{platt_english_2018}.
For information about edit history, we used a publicly-available data set containing
metadata (time, article id, user) about all edits from July 12, 2006 to December 2, 2015.
We used a custom script to scrape article quality assessments from logs produced
by WP 1.0 Bot for 2279 unique WikiProjects
between May 4, 2006 and December 2, 2015.
Finally, we used a publicly-available database dump of page events (including rename events)
to reconstruct the article id for each title mentioned in the assessment logs.

@@

In this paper, we have described the relationship between the structural properties of WikiProject
coeditor networks, their performance, and their efficiency.
As in other studies, we see a trade-off between performance and efficiency.
However, 
some properties, such as low degree, are associated with
both higher performance and higher efficiency.
We also find that the correlations between path length and performance are consistent with a conformity-based
social learning strategy, but not a greedy best-neighbor strategy.
We observe improved performance in more decentralized projects,
as has been seen in small-scale lab experiments.
We have also proposed a novel local majority learning strategy that is more realistic,
more efficient, and higher performance than existing strategies.
While most previous social learning simulations focus on path length,
we observe degree-dependent performance and efficiency
in both the local majority strategy
and a localized version of the conformity strategy.
We find that the direction of that dependence varies with the
specific strategy being used.
While additional work is needed to determine causal relationships
and the generalizability of our results,
we have shown evidence that several phenomena predicted by numerical
and small-scale lab experiments are present in a large,
real-world collaboration.
Our results suggest that the success of large-scale collaborations may be aided
by greater decentralization,
consensus or conformity-based decision-making,
and more tightly-knit collaborations between smaller teams.

@@

\bibliographystyle{aaai}
\bibliography{wp-eff-perf}
\end{document}
